---
title: "Peer Assessment 1"
author: "Lhall10"
date: "Sunday, June 14, 2015"
output: html_document
---

## Loading and Processing the Data

Here is the code which loads the data:

```{r}
setwd("C:/Users/user/Desktop/Coursera Data Science Sequence/Reproducible")
data <- read.csv("./activity.csv")
data2 <- na.omit(data)
```

##Mean Total Number of Steps Taken per Day
Here is the histogram for the total steps per day:

```{r}
totalsteps<-tapply(data2$steps, data2$date, sum)

hist(totalsteps)
```



Here is the median and the mean for the total steps per day:

```{r}
mean(data2$steps)

median(data2$steps)
```


##Average Daily Activity pattern
Here is the time series plot for the average number of steps taken:

```{r}
avg <- tapply(data2$steps, data2$interval, mean)
intavg<-as.data.frame(avg)
intavg$interval <- data2[1:288,3]
plot(x = intavg$interval, y = intavg$avg, type = "l", xlab = "Interval", ylab = "Average Steps")
```

Here is the 5-minute interval which contains the largest average number of steps:

```{r}
subset(intavg, intavg$avg == max(intavg$avg))
```

##Inputing missing values
Here is the total number of missing values:

```{r}
sum(is.na(data))
```

Here the code which fills in the missing values using the average number of steps per interval:

```{r}
data[is.na(data)]<- avg
```
Here is the histogram, mean, and median for the total number of steps taken for the completed data set:

```{r}
totalsteps2<-tapply(data$steps, data$date, sum)

hist(totalsteps2)

mean(data$steps)

median(data$steps)
```


The results from the complete data set do not appear to be very different from those generated from the incomplete data set


##Differences in Activity Patterns between Weekdays and Weekends
Here is how to create a new factor variable which will differentiate between weekends and weekdays:

```{r}
data$date <- as.Date(data$date)
wedays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
enddays <- c("Saturday", "Sunday")
data$day <- weekdays(data$date)
data$day[data$day %in% wedays] <- "weekday"
data$day[data$day %in% enddays] <- "weekend"
data$day <- as.factor(data$day)
```

Here is a panel plot comparing activity patterns between the two time frames:

```{r}
library(lattice)

xyplot(steps ~ interval|day, data = data, type = "a")
```
